Linear and Differential Cryptanalysis of DES

### 2009-02-01 trunk/talk/draft1.tex
Some fixes to linear slides, new figures, and a bit more conclusion.

\vspace{5mm}
\begin{columns}
\begin{column}{0.3\textwidth}
\begin{figure}
\includegraphics[width=0.7\textwidth]{spn_sbox_unkeyed.jpg}
\end{figure}
\end{column}

@@

\vspace{5mm}
\onslide<2->{Note also that $U_1 = P \oplus K_1$.}
\end{column}
\begin{column}{0.6\textwidth}
\begin{figure}
\includegraphics[height=0.45\textheight]{spn_single_round.jpg}
\end{figure}
\end{column}
\end{columns}

@@

\begin{frame}
Actual attack on SPN ... Demo ...
\end{frame}

@@

\begin{frame}
The actual Attack on 4 round DES ... Demo ...
\end{frame}

@@

\subsection{Links between the Attacks}
\begin{frame}
Links between Linear and Differential Attacks ...

@@

\begin{frame}
If you are building a cryptosystem ... To Do / Not To Do ...

\begin{frame}
Questions ... Doubts ... Coding ... Misc ... Discussion ...

>>>>

\vspace{5mm}
\begin{columns}
\begin{column}{0.3\textwidth}
\begin{figure}
\includegraphics[width=0.7\textwidth]{spn_sbox_X23_Y134.PNG}
\end{figure}
\end{column}

@@

\vspace{5mm}
\onslide<2->{Note also that $U_1 = P \oplus K_1$.}
\end{column}
\begin{column}{0.6\textwidth}
\begin{figure}
\includegraphics[height=0.45\textheight]{spn_round_expand.PNG}
\end{figure}
\end{column}
\end{columns}

@@

\begin{frame}
DEMO: Attack on 4-round SPN
\end{frame}

@@

\begin{frame}
DEMO: Attack on 4-round DES
\end{frame}

@@

\subsection{Links between the Attacks}
\begin{frame}
Linear Resistance:\\
\vspace{5mm}
Thm: A function $F: GF(2)^p \rightarrow GF(2)^q$is perfect nonlinear (ie bias is 0) if and only if it is \textit{bent}. \\
\vspace{3mm}
Thm: Bent functions exist only for $p \geq 2q$ and $p$ even. 
\vspace{5mm}
\end{frame}

@@

\begin{frame}
The problems of DES originated in two aspects:
\begin{itemize}
\item{6 bit S-Boxes are too easy to identify with linear or affine functions with high bias}
\item{Diffusion between rounds is just not fast enough}
\end{itemize}
AES, which replaced DES, provides an 8-Bit S-Box in the SubBytes step and higher diffusion through the ShiftRows and MixColumns steps. 
\end{frame}

\begin{frame}
References:\\
\vspace{5mm}
Matsui\\
Beham, Shamir\\
Heys
Chabaud, Vaudenay\\
Manferdelli
\end{frame}

\begin{frame}
\begin{center}
The End.\\
Questions?
\end{center}
\end{frame}
